Full Article Review

### 2024-10-21 doc/charting/Dora-2024.qmd

---
title: 'Turoman-2022'
---

::: content-hidden
fill in one form per paper. Name the form according to first author and
year like this: "Turoman-2022". Copy-paste the information from the
full-text review below.
:::

# Open and reproducible practices in developmental psychology research: The workflow of the WomCogDev lab as an example

-   File: data/review/fulltext/oa-id-W4229452124.pdf
-   DOI: https://doi.org/10.31234/osf.io/73bwu
-   OpenAlex ID: https://openalex.org/W4229452124

@@

@@

@@

>>>>

---
title: 'Dora-2024'
---

# Accelerating addiction research via Open Science and Team Science

-   File: data/review/fulltext/oa-id-W4383376256.pdf
-   DOI: https://doi.org/10.31234/osf.io/pbkrx
-   OpenAlex ID: https://openalex.org/W4383376256

@@

-   Used anonymous polls to make critical decisions in a large
    collaborative project
-   Important to setup a structure for leadership of the project and
    that the leadership is held accountable to decisions made
-   setup a structure to regularly ask for formal and informal feedback
    from members

@@

-   Education in open science needed to increase uptake

@@

-   no open science standards in journals
-   few opportunities for registered reports
-   there are few incentives to collaborate in large teams
-   grants are often given to an individual not a team

### 2024-10-21 doc/reviews/daniel.qmd
small updates on review file

Tools to use.

@@

-   This paper is not much about open collaboration but more about which
    tools to use for open and reproducible research from start to finish
    of a project.

@@

-   practical setup of collaboration

@@

-   data sharing

@@

-   this paper is mostly about a database for sharing spinal injury
    data. There are some points for how to improve sharing but not much
    about open collaboration
-   open data commons for spinal injury
-   Studies based on game theory suggest that data sharing might be
    beneficial if a collaborative approach is taken and data sharing is
    embraced as a community rather than by individuals
-   key events for the collaboration to be possible: - introduction of
    FAIR principles, update from funders, funding given to specific
    projects
-   Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to
    share tabular data of research in the field of spinal cord injury
-   Aim of the paper: to illustrate how members of research communities
    can work together toward the development of dedicated data sharing
    initiatives under the umbrella of FAIR
-   clearly highlighted the value of the massive demonstration/work for
    beta testing the site to reveal unforeseen problems
-   Moreover, participants pointed out the need for improving
    self-explanatory tutorials and help materials that would facilitate
    the learning experience for those who could not attend the workshop
-   "Registered users can request to become ODC-SCI Community members
    with further approval by the Leadership team." The most permissive
    account type is becoming an ODC-SCI Community member associated to
    an ODC-SCI lab, known as a Lab member

@@

-   recommendations
-   training

@@

@@

-   aim of the survey is to inform training priorities for open science
-   research cycle: planning, conducting, analysing, disseminating
-   Planning: team science guides, research co-production
-   Conducting: open research testing platforms, electronic
-   Most resources focus on the planning and analysing stage
-   Many resources were only for internal use
-   Very few ressources for open collaboration, none were open and they
    were valued poorly compared to other practices

@@

-   training
-   recommendations

@@

-   large-scale collaboration

@@

-   guide
-   workflow

@@

-   team science
-   example

@@

@@

-   tools
-   large-scale collaboration

@@

-   workflow

>>>>

-   tools
-   organization

@@

-   This paper is not much about open collaboration but more about which
    tools to use for open and reproducible research from start to finish
    of a project.
-   Study inception, planning, and ethics: OSF pre-registration,
    clinicaltrials.gov, aspredicted
-   Data processing and analysis: git, github, gitlab, etc
-   Scientific research can now become more transparent, inclusive and
    collaborative throughout the research cycle
-   Publishing Code of Conduct for collaborative projects is one
    practice that helps ensure a more welcoming and inclusive space for
    everyone regardless of background or identity

@@

-   collaboration structure
-   tools
-   organization

@@

-   data sharing
-   organization

@@

-   this paper is mostly about a database for sharing spinal injury
    data. There are some points for how to improve sharing but not much
    about open collaboration
-   open data commons for spinal injury
-   studies based on game theory suggest that data sharing might be
    beneficial if a collaborative approach is taken and data sharing is
    embraced as a community rather than by individuals
-   key events for the collaboration to be possible: - introduction of
    FAIR principles, update from funders, funding given to specific
    projects
-   Open Data Commons for SCI (ODC-SCI, odc-sci.org), a platform to
    share tabular data of research in the field of spinal cord injury
-   Aim of the paper: to illustrate how members of research communities
    can work together toward the development of dedicated data sharing
    initiatives under the umbrella of FAIR
-   clearly highlighted the value of the massive demonstration/work for
    beta testing the site to reveal unforeseen problems
-   Moreover, participants pointed out the need for improving
    self-explanatory tutorials and help materials that would facilitate
    the learning experience for those who could not attend the workshop
-   "Registered users can request to become ODC-SCI Community members
    with further approval by the Leadership team." The most permissive
    account type is becoming an ODC-SCI Community member associated to
    an ODC-SCI lab, known as a Lab member

@@

-   organization
-   training

@@

-   survey
-   recommendations

@@

-   aim of the survey is to inform training priorities for open science
-   research cycle: planning, conducting, analysing, disseminating
-   Planning: team science guides, research co-production
-   Conducting: open research testing platforms
-   Most resources focus on the planning and analysing stage
-   Many resources were only for internal use
-   Very few resources for open collaboration, none were open and they
    were valued poorly compared to other practices

@@

-   training
-   recommendations
-   organization

@@

-   large-scale collaboration
-   organization
-   tools

@@

-   tools
-   workflow

@@

-   organisation

@@

-   guide
-   example

@@

-   tools
-   organization
-   large-scale collaboration

@@

-   workflow
-   tools
